Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-28 paper/main.tex
clearer justification for k = 100 topics for embeddings

Knowledge estimates need not be limited to the content of the lectures. As
illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
estimating knowledge from a small number of quiz questions may be applied to
\textit{any} content, given its text embedding coordinate. To visualize how
knowledge ``spreads'' through text embedding space to content beyond the
lectures participants watched, we first fit a new topic model to the lectures'
sliding windows with $k = 100$ topics. We hoped that increasing the number of
topics from 15 to 100 might help us to generalize the knowledge predictions.
(Aside from increasing the number of topics from 15 to 100, all other
procedures and model parameters were carried over from the preceding analyses.)
As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
and projected each question into a shared text embedding space.

>>>>

Knowledge estimates need not be limited to the content of the lectures. As
illustrated in Figure~\ref{fig:knowledge-maps}, our general approach to
estimating knowledge from a small number of quiz questions may be applied to
\textit{any} content, given its text embedding coordinate. To visualize how
knowledge ``spreads'' through text embedding space to content beyond the
lectures participants watched, we first fit a new topic model to the lectures'
sliding windows with (up to)~$k = 100$~topics.
Conceptually, increasing the number of topics used by the model functions to
increase the ``resolution'' of the embedding space, providing a greater ability to
estimate knowledge for content that is highly similar to (but not precisely the same as)
that contained in the lectures.
Aside from increasing the number of topics from 15 to 100, all other
procedures and model parameters were carried over from the preceding analyses.
As in our other analyses, we resampled each lecture's topic trajectory to 1~Hz
and projected each question into a shared text embedding space.
